Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Discuss Cucumber

\begin{itemize}
    \item \emph{optional}: Bridging the gap between HUnit and QuickCheck
    \item
        Feedback for failing QuickCheck properties is not always as
        useful as it could be -> combinators that use QuickCheck's
        Result type could help
    \item
        Are more high-lever approaches to BDD, akin to Ruby's
        Cucumber, applicable to Haskell? (Observation: Cucumber's
        approach is tightly tied to OO)
\end{itemize}

>>>>

\begin{itemize}
    \item
        Feedback for failing QuickCheck properties is not always as
        useful as it could be -> combinators that use QuickCheck's
        Result type could help
    \item
\end{itemize}

\begin{quote}
    TBD: add ``The Cucumber Book'' to the bibliography as {\tt
    cucumber-book}.
\end{quote}

Cucumber~\cite{cucumber-book} is a higher-level approach to BDD for Ruby, and
it is typically used in combination with RSpec.
It focuses on user stories, to assist the developer in delivering
value to the stakeholder.
There is nothing comparable to Cucumber for Haskell yet.  And we think
it would be interesting to explore, whether it is possible to apply
Cucumber's approach to BDD to Haskell.

Are more high-lever approaches to BDD, akin to Ruby's Cucumber,
applicable to Haskell? (Observation: Cucumber's approach is tightly
tied to OO)
